---
title: "Mini-Project 2"
author: "Julianna Alvord and Peyton Draper"
date: "October 31, 2017"
output: html_document
---

#Sequels Using SQL
```{r, include = FALSE}
library(tidyverse)
library(ggplot2)

install.packages("mdsr")
# do NOT install RMySQL if you are on the RStudio Server
install.packages("RMySQL")

library(dplyr)
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")

#Tables within IMDB database!
dbListTables(db)

#Listing variables in a table!
dbListFields(db, "info_type")

#Visualizing tables as an example
#movie_link table tells what is a sequel
sql <- "
SELECT *
FROM info_type;
"
info_type_tb <- db %>%
  dbGetQuery(sql)
View(info_type_tb)
```

```{r, include = FALSE}
#Example code <- Find your fav movie!
sql <- "
SELECT t.title, t.production_year
FROM title t 
WHERE t.title LIKE '%Stick It%'
  AND t.kind_id = 1
ORDER BY production_year;
"
db %>%
  dbGetQuery(sql)
```

#All of the movies that are made in US each year
```{r}
sql <- "
<<<<<<< HEAD
SELECT t.id AS Movie_id1, t.title AS Title_1, t.production_year AS Production_Year, t.kind_id, m.movie_id AS Movie_id2, m.linked_movie_id, m.link_type_id, l.id AS Type_of_sequal, l.link, t2.id AS Movie_id3, t2.title AS Title_2, k.id AS Is_it_a_movie, k.kind AS Movie, i.info_type_id Gross_id, i.info AS Gross, i.movie_id AS Movie_id_4, i2.info_type_id AS Country_id, i2.info AS Country, i.movie_id AS Movie_id5
=======
SELECT count(DISTINCT t.id) as count, production_year
FROM title t
JOIN movie_info mi ON mi.movie_id = t.id
WHERE production_year <= 2017
AND kind_id = 1
AND info_type_id = 8
AND info LIKE '%USA%'
GROUP BY production_year;
"

total_US_movies <- db %>%
  dbGetQuery(sql)
```

#All of the sequels that are made in US each year
```{r}
sql2 <- "
SELECT count(DISTINCT t.id) as count, t.production_year
>>>>>>> 0459a3909d21cce15cfd487cb08cc428c6dff94f
FROM movie_link m
JOIN title t ON t.id = m.movie_id
JOIN title t2 on t2.id = m.linked_movie_id
JOIN link_type l ON l.id = m.link_type_id
JOIN kind_type k ON k.id = t.kind_id
<<<<<<< HEAD
JOIN movie_info i ON i.movie_id = m.movie_id
JOIN movie_info i2 ON i2.movie_id = m.movie_id
WHERE k.kind = 'movie'
AND i.info_type_id = 107
AND i2.info_type_id = 8
AND l.id IN (1, 2, 3, 4, 9, 10, 13);
"

table_1 <- db %>%
  dbGetQuery(sql)
```

#Making a graph
```{r}
table_1$Gross <- sub(" .*", "", table_1$Gross)

table_1_us <- table_1 %>%
  filter(Country == "USA")

table_1_us$Gross <- sub('.', '', table_1_us$Gross)

# table_1_us$Gross <- substring(table_1_us$usertweet, 3)

table_1_us$Gross <- as.numeric(table_1_us$Gross)
```

=======
JOIN movie_info mi ON mi.movie_id = t.id
WHERE k.kind = 'movie'
AND t.production_year <= 2017
AND l.id IN (1, 2, 3, 4, 9, 10, 13)
AND mi.info_type_id = 8
AND info LIKE '%USA%'
GROUP BY t.production_year;
"

sequel_US_movies <- db %>%
  dbGetQuery(sql2)
```

#All of the revenue made by any US movie each year
```{r}
sql3 <- "
SELECT t.id, production_year, substring_index(mi.info, '$', -1) as revenue
FROM movie_info mi
JOIN title t ON t.id = mi.movie_id
WHERE production_year <= 2017
AND kind_id = 1
AND mi.info_type_id = 107
AND mi.info LIKE '%USA%'
AND mi.info NOT Like '%Non-USA%'
AND mi.info NOT LIKE '%Worldwide%';
"

total_US_revenue <- db %>%
  dbGetQuery(sql3)
```

#All of the revenue made by any US sequel each year
```{r}
sql4 <- "
SELECT DISTINCT t.id, t.title, t.production_year, mi.info
FROM movie_link m
JOIN title t ON t.id = m.movie_id
JOIN title t2 on t2.id = m.linked_movie_id
JOIN link_type l ON l.id = m.link_type_id
JOIN kind_type k ON k.id = t.kind_id
JOIN movie_info mi ON mi.movie_id = t.id
WHERE k.kind = 'movie'
AND t.production_year <= 2017
AND l.id IN (1, 2, 3, 4, 9, 10, 13)
AND mi.info_type_id = 107
AND mi.info LIKE '%USA%'
AND mi.info NOT Like '%Non-USA%'
AND mi.info NOT LIKE '%Worldwide%';
"

sequel_US_revenue <- db %>%
  dbGetQuery(sql4)
```
>>>>>>> 0459a3909d21cce15cfd487cb08cc428c6dff94f
