---
title: "Mini-Project 2"
author: "Julianna Alvord and Peyton Draper"
date: "October 31, 2017"
output: html_document
---

#Sequels Using SQL
```{r, include = FALSE}
library(tidyverse)
library(ggplot2)

library(extrafont)

font_import(pattern="[A/a]rial")

font_import(pattern = '[L/l]inotype')

setwd("/Library/Fonts/Microsoft/Garamond")

extrinstall.packages("mdsr")
# do NOT install RMySQL if you are on the RStudio Server
install.packages("RMySQL")

library(dplyr)
library(mdsr)
library(RMySQL)
db <- dbConnect_scidb(dbname = "imdb")

#Tables within IMDB database!
dbListTables(db)

#Listing variables in a table!
dbListFields(db, "info_type")

#Visualizing tables as an example
#movie_link table tells what is a sequel
sql <- "
SELECT *
FROM kind_type
LIMIT 0, 100;
"
kind_type_tb <- db %>%
  dbGetQuery(sql)
View(kind_type_tb)
```

```{r, include = FALSE}
#Example code <- Find your fav movie!
sql <- "
SELECT t.title, t.production_year
FROM title t 
WHERE t.title LIKE '%Stick It%'
  AND t.kind_id = 1
ORDER BY production_year;
"
db %>%
  dbGetQuery(sql)
```

#All of the movies that are made in US each year
```{r}
sql <- "
SELECT t.id AS Movie_id1, t.title AS Title_1, t.production_year AS Production_Year, t.kind_id, m.movie_id AS Movie_id2, m.linked_movie_id, m.link_type_id, l.id AS Type_of_sequal, l.link, t2.id AS Movie_id3, t2.title AS Title_2, k.id AS Is_it_a_movie, k.kind AS Movie, i.info_type_id Gross_id, i.info AS Gross, i.movie_id AS Movie_id_4, i2.info_type_id AS Country_id, i2.info AS Country, i.movie_id AS Movie_id5"

sql <- "
SELECT count(DISTINCT t.id) as count, production_year
FROM title t
JOIN movie_info mi ON mi.movie_id = t.id
WHERE production_year <= 2017
AND kind_id = 1
AND info_type_id = 8
AND info LIKE '%USA%'
GROUP BY production_year;
"

total_US_movies <- db %>%
  dbGetQuery(sql)
```

#All of the sequels that are made in US each year
```{r}
sql2 <- "
SELECT count(DISTINCT t.id) as count, t.production_year
>>>>>>> 0459a3909d21cce15cfd487cb08cc428c6dff94f
FROM movie_link m
JOIN title t ON t.id = m.movie_id
JOIN title t2 on t2.id = m.linked_movie_id
JOIN link_type l ON l.id = m.link_type_id
JOIN kind_type k ON k.id = t.kind_id
<<<<<<< HEAD
JOIN movie_info i ON i.movie_id = m.movie_id
JOIN movie_info i2 ON i2.movie_id = m.movie_id
WHERE k.kind = 'movie'
AND i.info_type_id = 107
AND i2.info_type_id = 8
AND l.id IN (1, 2, 3, 4, 9, 10, 13);
"

table_1 <- db %>%
  dbGetQuery(sql)
```

#Making a graph
```{r}
table_1$Gross <- sub(" .*", "", table_1$Gross)

table_1_us <- table_1 %>%
  filter(Country == "USA")

table_1_us$Gross <- sub('.', '', table_1_us$Gross)

# table_1_us$Gross <- substring(table_1_us$usertweet, 3)

table_1_us$Gross <- as.numeric(table_1_us$Gross)
```

=======
```{r}
sql2 <- "
SELECT count(DISTINCT t.id) as count, t.production_year
JOIN movie_info mi ON mi.movie_id = t.id
WHERE k.kind = 'movie'
AND t.production_year <= 2017
AND l.id IN (1, 2, 3, 4, 9, 10, 13)
AND mi.info_type_id = 8
AND info LIKE '%USA%'
GROUP BY t.production_year;
"

sequel_US_movies <- db %>%
  dbGetQuery(sql2)
```

#All of the revenue made by any US movie each year
```{r}
sql3 <- "
SELECT t.id, production_year, substring_index(mi.info, '$', -1) as revenue
FROM movie_info mi
JOIN title t ON t.id = mi.movie_id
WHERE production_year <= 2017
AND kind_id = 1
AND mi.info_type_id = 107
AND mi.info LIKE '%USA%'
AND mi.info NOT Like '%Non-USA%'
AND mi.info NOT LIKE '%Worldwide%';
"

total_US_revenue <- db %>%
  dbGetQuery(sql3)
```

#All of the revenue made by any US sequel each year
```{r}
sql4 <- "
SELECT DISTINCT t.id, t.title, t.production_year, mi.info
FROM movie_link m
JOIN title t ON t.id = m.movie_id
JOIN title t2 on t2.id = m.linked_movie_id
JOIN link_type l ON l.id = m.link_type_id
JOIN kind_type k ON k.id = t.kind_id
JOIN movie_info mi ON mi.movie_id = t.id
WHERE k.kind = 'movie'
AND t.production_year <= 2017
AND l.id IN (1, 2, 3, 4, 9, 10, 13)
AND mi.info_type_id = 107
AND mi.info LIKE '%USA%'
AND mi.info NOT Like '%Non-USA%'
AND mi.info NOT LIKE '%Worldwide%';
"

sequel_US_revenue <- db %>%
  dbGetQuery(sql4)
```
>>>>>>> 0459a3909d21cce15cfd487cb08cc428c6dff94f





####################################################################






#All of the movies that are made in US each year
```{r}
sql <- "
SELECT count(DISTINCT(t.id)) as count_movie, production_year
FROM title t
JOIN movie_info mi ON mi.movie_id = t.id
JOIN kind_type k ON k.id = t.kind_id
WHERE production_year <= 2017
AND k.kind = 'movie'
AND mi.info_type_id = 8
AND info LIKE '%USA%'
GROUP BY production_year;
"

total_US_movies <- db %>%
  dbGetQuery(sql)
```


#All of the sequels that are made in US each year
```{r}
sql2 <- "
SELECT count(DISTINCT(t.id)) as count_sequals, t.production_year
FROM movie_link m
JOIN title t ON t.id = m.movie_id
JOIN title t2 on t2.id = m.linked_movie_id
JOIN link_type l ON l.id = m.link_type_id
JOIN kind_type k ON k.id = t.kind_id
JOIN movie_info mi ON mi.movie_id = t.id
WHERE k.kind = 'movie'
AND t.production_year <= 2017
AND l.id IN (1, 2, 3, 4, 13, 14)
AND mi.info_type_id = 8
AND info LIKE '%USA%'
GROUP BY t.production_year;
"

sequel_US_movies <- db %>%
  dbGetQuery(sql2)
```


#All of the revenue made by any US movie each year NO NO NO
```{r}
# sql3 <- "
# SELECT t.id, t.title, production_year, SUM(replace(substring_index(substring_index(mi.info, '$', -1), ' ', 1), ',', '')) as revenue
# FROM movie_info mi
# JOIN title t ON t.id = mi.movie_id
# WHERE production_year <= 2017
# AND kind_id = 1
# AND mi.info_type_id = 107
# AND mi.info LIKE '%USA%'
# AND mi.info NOT Like '%Non-USA%'
# AND mi.info NOT LIKE '%Worldwide%'
# GROUP BY production_year;
# "
# 
# total_US_revenue <- db %>%
#   dbGetQuery(sql3)
```


#All of the revenue made by any US sequel each year
```{r}
sql4 <- "
SELECT DISTINCT t.id, t.title, t.production_year, SUM(replace(substring_index(substring_index(mi.info, '$', -1), ' ', 1), ',', '')) as revenue_Sum
FROM movie_link m
JOIN title t ON t.id = m.movie_id
JOIN title t2 on t2.id = m.linked_movie_id
JOIN link_type l ON l.id = m.link_type_id
JOIN kind_type k ON k.id = t.kind_id
JOIN movie_info mi ON mi.movie_id = t.id
WHERE k.kind = 'movie'
AND t.production_year <= 2017
AND l.id IN (1, 2, 3, 4, 13, 14)
AND mi.info_type_id = 107
AND mi.info LIKE '%USA%'
AND mi.info NOT Like '%Non-USA%'
AND mi.info NOT LIKE '%Worldwide%'
GROUP BY t.production_year;
"

sequel_US_revenue <- db %>%
  dbGetQuery(sql4)
```

#ALL MOVIES REVENUE
```{r}
sql4 <- "
SELECT DISTINCT t.id, t.title, t.production_year, SUM(replace(substring_index(substring_index(mi.info, '$', -1), ' ', 1), ',', '')) as revenue_Sum_all
FROM movie_link m
JOIN title t ON t.id = m.movie_id
JOIN title t2 on t2.id = m.linked_movie_id
JOIN link_type l ON l.id = m.link_type_id
JOIN kind_type k ON k.id = t.kind_id
JOIN movie_info mi ON mi.movie_id = t.id
WHERE k.kind = 'movie'
AND t.production_year <= 2017
AND mi.info_type_id = 107
AND mi.info LIKE '%USA%'
AND mi.info NOT Like '%Non-USA%'
AND mi.info NOT LIKE '%Worldwide%'
GROUP BY t.production_year;
"

ALL_MOVIES_US_revenue <- db %>%
  dbGetQuery(sql4)
```



#TOTAL all movies
```{r}
# sql2 <- "
# SELECT count(DISTINCT t.id) as count_sequals, t.production_year
# FROM movie_link m
# JOIN title t ON t.id = m.movie_id
# JOIN title t2 on t2.id = m.linked_movie_id
# JOIN link_type l ON l.id = m.link_type_id
# JOIN kind_type k ON k.id = t.kind_id
# JOIN movie_info mi ON mi.movie_id = t.id
# WHERE k.kind = 'movie'
# AND t.production_year <= 2017
# AND mi.info_type_id = 8
# AND info LIKE '%USA%'
# GROUP BY t.production_year;
# "
# 
# TOTAL_US_movies <- db %>%
#   dbGetQuery(sql2)
```

#Creating the table and making graph!
```{r, message=FALSE}
Graph_table <- ALL_MOVIES_US_revenue %>%
  full_join(sequel_US_revenue, by = "production_year") %>%
  full_join(sequel_US_movies, by = "production_year") %>%
  full_join(total_US_movies, by = "production_year") %>%
  filter(production_year >= 1955) %>%
  filter(production_year <2017) %>%
  mutate(percent_rev = (revenue_Sum / revenue_Sum_all)*100, percent_seq = (count_sequals / count_movie)*100) %>%
  group_by(production_year) %>%
  summarise(percent_rev = (revenue_Sum / revenue_Sum_all)*100,
            percent_seq = (count_sequals / count_movie)*100)


ggplot(Graph_table, aes(production_year, percent_rev)) + 
  geom_line(aes(y = percent_rev, colour = "percent_rev"), size = 0.3) +
  geom_smooth(aes(y = percent_rev, colour = "percent_rev"), se = FALSE, size = 1.3) +
  geom_line(aes(y = percent_seq, colour = "percent_seq"), size = 0.3) +
  geom_smooth(aes(y = percent_seq, colour = "percent_seq"), se = FALSE, size = 1.3) +
  theme(legend.title = element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black", size = 0.2), axis.text.x = element_text(colour="grey20",size=10, family = "Palatino Linotype"), axis.text.y = element_text(color = "grey20", size =10, family = "Palatino Linotype"), axis.title.x = element_text(vjust=-.55, family = "Palatino Linotype" ), axis.title.y = element_text(vjust = .55, family = "Palatino Linotype"), plot.title = element_text(hjust = 0.5, family = "Palatino Linotype"), panel.background = element_rect(fill = 'white'), legend.text = element_text(family = "Palatino Linotype", size = 10)) +
  labs(x="Year", y="Percentage") +
  scale_y_discrete(limits = c(0, 5, 10, 15, 19),
                   labels = c("0%", "5%", "10%", "15%", "19%")) +
  scale_x_discrete(limits = c(1960, 1980, 2000, 2017),
                   labels = c("1960", "1980", "2000", "2017")) +
  ggtitle("More Sequels Than Ever? Only in the Studios Making $$$") +
  scale_color_manual(values = c("goldenrod3", "red4"),
                    breaks=c("percent_rev", "percent_seq"),
                    labels=c("Sequel Revenue Percentage", "N of Sequels Percentage"))
```

